Verifying Demonstrations

### 2017-08-25 properties.tex
Edits privacy section

@@

\begin{frame}
  \begin{question}
    Will such a signature scheme solve both problems?
  \end{question}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
  \begin{question}
    What Alice submits her proof, stores the hash of the block, removes proof 
    and signature key?
  \end{question}
\end{frame}

@@

\begin{frame}
  \begin{question}
    Shall we offer a platform that is run by a variety of institutions who 
    offers to verify protests?
    Or go strictly peer-to-peer?
  \end{question}
  \begin{question}
    If strictly peer-to-peer, and only run by protesters, one can infer that 
    they are protesters by running such a node.
    Can this be mitigated?
  \end{question}
\end{frame}

>>>>

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Unique ring signatures~\cite{UniqueRingSignatures} has this 
        property: two signatures are linked with high probability.
      \item We need keys strongly tied to identities to prevent Sybil.
    \end{itemize}
  \end{remark}

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}
\end{frame}

@@

\begin{frame}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}

  \begin{remark}
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
    \end{itemize}
  \end{remark}
\end{frame}

@@

\begin{question}
  Shall we offer a platform that is run by a variety of institutions who 
  offers to verify protests?
  Or go strictly peer-to-peer?
\end{question}

\begin{question}
  If strictly peer-to-peer, and only run by protesters, one can infer that 
  they are protesters by running such a node.
  Can this be mitigated?
\end{question}
